\documentclass{res} 

\usepackage{geometry}

\setlength{\voffset}{-1.2in}
\setlength{\hoffset}{0.1in}

\begin{document}
\vbox{
\begin{center}
{\bf\huge Stephen W. McArdle } \\
837 Hudson Street | Hoboken, NJ 07030 | (732) 977-6592 | stephenwmcardle@gmail.com\\
stephenmcardle.com
\end{center}

\section{\bf\large Summary}
Adaptable, motivated, and responsible senior Computer Science student at a renowned technical university with experience in web development, data science, research, and algorithm design, with advanced skillsets in Python, Javascript, Node.js, and database management systems, both SQL and NoSQL. Currently looking to begin a full-time position in Summer 2018.

\section{\bf\large Technical Experience}

{\sl Full-Stack Developer} \hfill October 2017 - Present \\
Turbo 360 \hfill New York, NY \\
Working with the MERN stack and producing reusable serverless functions to expand the Turbo 360 platform, such as a Text Metrics function that parses a given text and returns commons words, sentiment, processed versions of the text, and other data. Also helping new and experienced users become accustomed to programming in the Turbo environment by developing tutorials and workshops.

{\sl Full-Stack Developer} \hfill September 2017 - Present \\
Senior Design Marketplace \hfill Hoboken, NJ \\
Inventing a new system to revolutionize Senior Design courses at Stevens Institute of Technology. The website will allow professors, students, and clients to manage the entire project online from start to finish. This system will expedite and simplify the entire Senior Design process, as well as promote cross-discipline projects. The team uses Scrum along with the LAMP stack.

{\sl Lead Programmer} \hfill September 2017 - October 2017 \\
Co-authorship Network \hfill Hoboken, NJ \\
Compiled data from Scopus, a bibliographic database, and compared it to a database of Stevens faculty members to create a network of co-authorships amongst professors at Stevens. Developed network graphs using Python and Gephi in order to study co-authorships by gender and department.

{\sl Research Assistant} \hfill May 2017 - August 2017\\
Epidemic Disease Simulator \hfill Hoboken, NJ \\
Programmed a simulator designed to track the spread of epidemic diseases using Node.js. The project was based on a simulator called FRED, originally  written in C++ and released by the University of Pittsburgh. Efficiently leveraging the simulator required many optimizations of Javascript code and classes, which resulted in up to an 80\% decrease in run-time.

{\sl Lead Developer} \hfill May 2015 - Present \\
DCInbox \hfill Hoboken, NJ \\
Lead engineer and developer on the DCInbox project. Project involved maintaining over 100,000 e-newsletters sent from every member of Congress since August 2009. Filtered and processed email data using Python and R and created network graphs using Gephi. Demonstrated connections between members of Congress and sentiment towards President Obama. Presented research at the 2017 Southern Political Science Association Conference in New Orleans, LA.


\section{\bf\large Skills}
{\sl Coding: } Python, Javascript, Java, C/C++, React, HTML5, CSS3, R, SQL, LaTeX \\
{\sl Technologies:} Node.js, MongoDB, Linux, Git, AWS, Gephi, Windows, Microsoft Office

\section{\bf\large Honors \& Activities}
Upsilon Pi Epsilon - International Computer Science Honor Society - Inducted May 2016\\
Dean's List - Every semester while attending Stevens \\
Stevens Scholars Program - Admitted based on academic performance \\ %% consider rewording this
Phi Sigma Kappa Fraternity - Scholarship Chair Fall 2016 \& Spring 2017

\section{\bf\large Education}
Stevens Institute of Technology, B.S., Computer Science, expected May 2018 \hfill GPA: 3.61 / 4.00 \\
{\sl Selected Coursework:} Web Programming, Software Development, Database Management Systems, Data Structures, Advanced Algorithm Design, Team Programming, Discrete Structures

}
\end{document}